%-------------------------
% Resume in Latex
% Author : Sravan Balaji
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\resumeSkillItemHeading}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-4pt}}
  }
}

\newcommand{\resumeItem}[1]{
	\item\small{
		#1
	}
}

\newcommand{\resumeCompanyHeading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
    \end{tabular*}\vspace{-0pt}
}

\newcommand{\resumeJobHeading}[3]{
	\vspace{-1pt}
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		{\small#1} - {\small #2} & {\small #3} \\
	\end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeCompanyListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeCompanyListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  {\textbf{\Huge Sravan Balaji}}
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}lcr}
	   Email: \href{mailto:balajsra@umich.edu}{balajsra@umich.edu}
	   & Phone: (248) 417 - 0955
	   & LinkedIn: \href{https://www.linkedin.com/in/sravan-balaji/}{sravan-balaji}
	   & Website: \href{https://sravanbalaji.com/}{sravanbalaji.com}
  \end{tabular*}
\end{center}

%----------SUMMARY-----------------
\section{Summary}
U.S. Citizen with active security clearance. Experienced roboticist with a strong multi-disciplinary background interested in working on ground, air, and underwater autonomous systems. Passionate about solving challenging problems through the power of autonomy.

%-----------WORK EXPERIENCE-----------------
\section{Work Experience}

\resumeCompanyListStart
  % MITRE
  \resumeCompanyHeading{\href{https://mitre.org/}{MITRE}}{May 2021 - Present}
    \resumeJobHeading{Intermediate Autonomous Systems Engineer}{McLean, VA}{Sep. 2022 -- Present}

    \resumeJobHeading{Associate Autonomous Systems Engineer}{McLean, VA}{Jan. 2022 -- Sep. 2022}
    \resumeItemListStart
      \resumeItem{Led effort to take global path planning algorithm from research paper pseudo code, to Python prototype, to C++ and ROS implementation on a \href{https://clearpathrobotics.com/husky-unmanned-ground-vehicle-robot/}{Clearpath Husky UGV}; conducted testing in simulation with \href{https://gazebosim.org/home}{Gazebo} and on the live platform; successfully able to avoid obstacles while applying desired safety factors}
      \resumeItem{Developed an interface in Python to translate existing drone messaging protocols to \href{https://microsoft.github.io/AirSim/}{AirSim} API calls for seamless transition to new simulation setup}
      \resumeItem{Aided research effort into improving Test \& Evaluation of Artificial Intelligence}
    \resumeItemListEnd

    \resumeJobHeading{Graduate Navigation Intern}{Remote}{May 2021 -- Aug. 2021}
    \resumeItemListStart
      \resumeItem{Designed and developed approach to identify implicit mitigation links between nodes in a directed acyclic graph for PNT Defense \& Threat Library written in Python}
      \resumeItem{Revamped and formalized software development process to improve visibility and organization of PNT Assurance project written in Julia}
      \resumeItem{Placed 3rd in team-based machine learning intern hackathon; identified malicious URLs based on URL strings and information on age of domain; achieved 0.94 F1 score}
      \resumeItem{Placed top 3 in intern AWS DeepRacer challenge; trained reinforcement learning model to control simulated autonomous vehicle around unseen race tracks}
    \resumeItemListEnd

  % University of Michigan
  \resumeCompanyHeading{\href{https://umich.edu/}{University of Michigan - Ann Arbor}}{Jan. 2021 - Apr. 2021}
    \resumeJobHeading{NA 568 Grader}{Remote}{Jan. 2021 -- Apr. 2021}
    \resumeItemListStart
      \resumeItem{Graded assignments for NA 568: Mobile Robotics at the University of Michigan - Ann Arbor}
    \resumeItemListEnd

  % Rivian
  \resumeCompanyHeading{\href{https://rivian.com/}{Rivian}}{Jun. 2020 - Aug. 2020}
    \resumeJobHeading{ADAS Controls Intern}{Remote}{Jun. 2020 -- Aug. 2020}
    \resumeItemListStart
      \resumeItem{Supported creation of Model-in-Loop framework for production controls software components; tested ~50 requirements, identified and resolved 7 issues}
      \resumeItem{Integrated speed limit algorithm into production controls software for use with Simulink Coder C/C++ code generation; considerations made for embedded system processing limits and time delays}
      \resumeItem{Modified MATLAB data processing scripts to work with new test logs; compared performance against requirements and simulation to determine controls parameters to tune}
    \resumeItemListEnd

  % Hughes Network Systems
  \resumeCompanyHeading{\href{https://www.hughes.com/}{Hughes Network Systems}}{May 2019 - Aug. 2019}
    \resumeJobHeading{Software Development Intern}{San Diego, CA}{May 2019 -- Aug. 2019}
    \resumeItemListStart
      \resumeItem{Created Windows GUI app in C\# employing .NET framework; automated mobile terminal configuration process to reduce user involvement, prevent errors, and decrease configuration time}
      \resumeItem{Implemented location based services on terminal software written in C; leveraged MQTT-SN protocol to provide low-cost method of sending GPS data to server}
    \resumeItemListEnd

  % University of Michigan
  \resumeCompanyHeading{\href{https://umich.edu/}{University of Michigan - Ann Arbor}}{Sep. 2016 - Apr. 2019}
    \resumeJobHeading{Research Assistant in the \href{http://csdl.engin.umich.edu/}{Compliant Systems Design Lab}}{Ann Arbor, MI}{Jan. 2019 -- Apr. 2019}
    \resumeItemListStart
      \resumeItem{Formulated and conducted an experiment to investigate applicability of digital image correlation (DIC) for analyzing strain in fiber reinforced elastomeric enclosures (FREEs)}
      \resumeItem{Manufactured a test setup to securely hold FREEs and control flow of compressed gas}
      \resumeItem{Created FREEs with varying parameters by hand to investigate their behaviour under pneumatic loads}
      \resumeItem{Developed a C++ program to analyze creep behavior of a FREE and generate plots}
    \resumeItemListEnd

    \resumeJobHeading{Intramural Sports Supervisor}{Ann Arbor, MI}{Sep. 2017 -- Dec. 2018}
    \resumeItemListStart
      \resumeItem{Voted Supervisor of the Year by peers for 2017-2018 school year}
      \resumeItem{Developed an excel macro to automate scheduling supervisor shifts; eliminated issues with transportation of people and equipment present in manual scheduling process}
      \resumeItem{Supervised intramural sports games at various facilities on campus; evaluated performance of officials to improve customer experience; resolved any disputes that arose}
    \resumeItemListEnd

    \resumeJobHeading{Intramural Sports Official}{Ann Arbor, MI}{Sep. 2016 -- Dec. 2018}
    \resumeItemListStart
      \resumeItem{Enforced the rules of the game for intramural soccer, flag football, and basketball matches between college students}
      \resumeItem{Managed flow the game to ensure customer enjoyment and safety}
    \resumeItemListEnd

  % Rivian
  \resumeCompanyHeading{\href{https://rivian.com/}{Rivian}}{May 2017 - Dec. 2018}
    \resumeJobHeading{Business Technology Intern}{Plymouth, MI}{May 2018 -- Dec. 2018}
    \resumeItemListStart
      \resumeItem{Championed effort to remove BOM data inconsistencies; developed Excel macro to summarize mass and cost data, alert PMs of incorrect data; resulted in faster detection and resolution of issues}
      \resumeItem{Introduced and designed an internal website to collect and display data from business systems utilizing Python and Django; worked with REST APIs to present reports of issues by severity}
      \resumeItem{Led effort to migrate IT team to a new service desk; worked with Jira Service Desk to automate triage and assignment of IT tickets; increased ticket resolution rate within SLA targets from 70\% to 95\%}
    \resumeItemListEnd

    \resumeJobHeading{Vehicle Integration Intern}{Livonia, MI}{May 2017 -- Aug. 2017}
    \resumeItemListStart
      \resumeItem{Created system architecture models to distribute and track requirements from system to component level}
      \resumeItem{Managed requirements in DOORS Next Generation and created custom reports to distribute requirements to sub-teams}
      \resumeItem{Developed a program in Java to summarize results of simulation; allowed users to modify inputs to see projected results of simulation to avoid additional testing and reduce costs}
    \resumeItemListEnd
\resumeCompanyListEnd

%--------PROJECTS------------
% \section{Projects}
% \resumeSubHeadingListStart

% 	% Reduce Reuse Recycle Robot
% 	\resumeSubheading
% 		{Reduce Reuse Recycle Robot}{Ann Arbor, MI}
% 		{EECS 467 Course Project (\href{https://eecs-467-w20-rrrobot-project.github.io/RRRobot/home}{GitHub: EECS-467-W20-RRRobot-Project/RRRobot})}{Mar. 2020 -- Apr. 2020}

% 		\resumeItemListStart

% 			\item Simulated UR10 robot arm with ROS and Gazebo that classifies and sorts items into trash and recycling

% 			\item Employed convolutional neural network to classify images, depth camera point cloud coordinate transformations to determine grip position, and inverse kinematics to calculate joint positions

% 		\resumeItemListEnd

% 	% Autonomous Delivery of scCO2
% 	\resumeSubheading
% 		{Autonomous Delivery of Supercritical CO\textsubscript{2}}{Canton, MI}
% 		{MECHENG 450 Course Project with \href{https://www.fusioncoolant.com/}{Fusion Coolant Systems}}{Sep. 2019 -- Dec. 2019}

% 		\resumeItemListStart

% 			\item Led team of 5 through entire design process for semester project: problem definition, concept generation and evaluation, final design prototyping and validation

% 			\item Performed engineering analysis, technical report writing, and CAD in SolidWorks; created engineering drawings, design review presentations, and physical prototype of final design

% 		\resumeItemListEnd

% \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}

\resumeCompanyListStart
  % UMICH
  \resumeCompanyHeading{\href{https://umich.edu/}{University of Michigan - Ann Arbor}}{Sep. 2016 - Dec. 2021}
    \resumeJobHeading{M.S. in Robotics; Focus in Acting; GPA: 3.982}{Ann Arbor, MI}{Jan. 2021 -- Dec. 2021}
    \resumeItemListStart
      \item{Mobile Robotics; Design of Digital Control Systems; Self Driving Cars; Robotic Systems Lab}
    \resumeItemListEnd

    \resumeJobHeading{B.S.E. in Mechanical Engineering; Focus in Controls; GPA: 3.776}{Ann Arbor, MI}{Sep. 2016 -- Dec. 2020}
    \resumeItemListStart
      \item{Automatic Control; Modeling, Analysis, and Control of Dynamic Systems}
    \resumeItemListEnd

    \resumeJobHeading{B.S.E. in Computer Science; Focus in Intelligent Systems; GPA: 3.776}{Ann Arbor, MI}{Sep. 2016 -- Dec. 2020}
    \resumeItemListStart
      \item{Autonomous Robotics Lab; Machine Learning; Computer Vision}
    \resumeItemListEnd
\resumeCompanyListEnd


%--------SKILLS------------
\section{Skills}
\resumeItemListStart

\resumeSkillItemHeading{Programming}
{\href{https://www.cplusplus.com/}{C/C++}, \href{https://www.python.org/}{Python}, \href{https://www.mathworks.com/products/matlab.html}{MATLAB}, \href{https://julialang.org}{Julia}, \href{https://www.javascript.com/}{JavaScript}, \href{https://docs.microsoft.com/en-us/dotnet/csharp/}{C\#}, \href{https://www.java.com/}{Java}}

% \resumeSkillItemHeading
% {Markup}
% {\href{https://www.latex-project.org/}{\LaTeX}, HTML, Markdown, \href{https://orgmode.org}{Org Mode}}

\resumeSkillItemHeading{Development}
{\href{https://www.linux.org}{GNU/Linux}, \href{https://git-scm.com}{Git}, \href{https://www.docker.com}{Docker}, \href{https://code.visualstudio.com/?wt.mc_id=DX_841432}{Visual Studio Code}, \href{https://www.gnu.org/software/emacs/}{GNU Emacs}, \href{https://www.vim.org}{Vim}, \href{https://atom.io}{Atom}, \href{https://visualstudio.microsoft.com/vs/}{Visual Studio}}

\resumeSkillItemHeading{Libraries/Frameworks}
{\href{https://www.ros.org/}{ROS}, \href{http://wiki.ros.org/move_base}{move\_base}, \href{https://numpy.org/}{NumPy}, \href{https://opencv.org}{OpenCV}, \href{https://pytorch.org/}{PyTorch}, \href{https://vuejs.org/}{Vue.js}, \href{https://getbootstrap.com/}{Bootstrap}, \href{https://gtsam.org/}{GTSAM}}

\resumeSkillItemHeading{Robotics/Autonomy}
{Controls, Path Planning, Kalman Filters, SLAM, GPS, Forward \& Inverse Kinematics, Machine Learning, Computer Vision}

\resumeSkillItemHeading{Computer Aided Design}
{\href{https://www.solidworks.com/}{SolidWorks},\href{https://www.3ds.com/products-services/catia/}{CATIA}}

% \resumeSkillItemHeading
% 	{Manufacturing}
% 	{University of Michigan Wilson Center Basic I $\&$ II, Mill Training}

\resumeSkillItemHeading{Languages}
{English (first language), French (conversational), Tamil (conversational)}

\resumeItemListEnd

%-------------------------------------------
\end{document}
